Untitled

### 2023-12-31 code/analysis_Redo.Rmd
better stratified access analysis

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)), 
  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 10% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

@@

>>>>

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)), 
  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 6) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 6) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 6) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 10% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 6) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

@@

## Stratified analysis instead for Access
```{r}

#### STRATIFEID ANALYSIS INSTEAD

model <- did2s(
      data = df.spill3  %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

TEs.strat.far <- data.frame(model$coeftable)[1,]

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 )
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.far <- rbind(TEs.strat.far, data.frame(model$coeftable)[1,])
}

model <- did2s(
      data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

TEs.strat.close <- data.frame(model$coeftable)[1,]

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 )
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.close <- rbind(TEs.strat.close, data.frame(model$coeftable)[1,])
}

cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[6:10,]

df.spill3  %>% filter(Dist > quantile(Dist, 0.9) ) %>% 
  filter(Att > 0) %>% 
  group_by(Tx) %>% 
  summarise(mean(Total.Hours))

df.spill3 %>% filter(Dist < quantile(Dist, 0.2)) %>% 
  filter(Att > 0) %>%
  summarise(mean(Total.Hours))

summary(lm(data = df.spill3 %>% filter(Att > 0 & Dist < 200), Total.Hours ~ Dist))

summary(df.spill3[df.spill3$Att > 0,]$Dist)

### REALLY IMPORTANT BACK OF THE ENVELOP CALCULATION

sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > 40 & Year == Att - 1) %>% select(Total.Hours))

# Funcationl form of ATT x distance for total hours.... 1.64 - 0.041 * DIST... which integrated from 40km to 200km is about 524 lost hours
# Divide that by the proceeding line leads to ~ 5% reallocation of resources
